---
title: "figure4_data_validation"
author: "Kaixin"
date: "2023-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Socialmedia_Mobility/")
```


```{r initial, include=FALSE}
library(tidyverse)
library(lubridate)
library(data.table)
library(sf)
library(janitor)
library(zoo)
library(ggtext)
library(patchwork)
options(datatable.print.nrows = 5)
```


```{r color_preset}
source("publication/color_setting.R")
```


```{r file_path}
ifile_CMI <- 
  "data/raw/figure4_Baidu_Qianxi_data/City_Movement_Intensity_202001-202004.csv"

ifile_checkins <-
  "data/processed/01_checkins.csv.gz"

ifile_city_adm <-
  "data/raw/figure3_adm_for_join.csv"

ifile_census_city <-
  "data/raw/figure4_census/result/01_census_city_level.csv"

ifile_city_abnormal <-
  "data/raw/"

odir_plot <-
  "publication/figure4_data_validation/"
```


```{r input data}
# Baidu CMI (city movement index)
# data is available for each city in China from 2020/01/01 to 2020/05/02
CMI <-
  fread(ifile_CMI, header = T) %>%
  setnames("GbCity_EN", "city") %>%
  melt(id.vars = "city",
       variable.name = "date",
       value.name = "CMI") %>%
  .[, date := ymd(date)] %>%
  .[, adcode := str_sub(city, start = -6, end = -1)] %>%
  .[order(adcode, date)]

checkins <-
  fread(ifile_checkins,
        select = c(userid = "character",
                   created_at = "Date",
                   city = "character",
                   category_google = "character"))

city_adm <-
  fread(ifile_city_adm,
        colClasses = c("character"))

census_city <-
  fread(ifile_census_city) %>%
  .[, .(native, pop_2020)]
```


```{r integrate_administrative_divisions_and_census}
adm_census <-
  merge(city_adm,
        census_city,
        all.x = T,
        by.x = "ct_name_2",
        by.y = "native") %>%
  # the proportion of the city population to the national population
  .[, pop_2020_prop_na := pop_2020/sum(pop_2020, na.rm = T)] %>%
  # # the proportion of the city population to the corresponding province population
  .[, pop_2020_prop_pr := pop_2020/sum(pop_2020, na.rm = T), by = .(pr_name)] %>%
  .[order(ct_adcode)]
```


# calcualte Weibo CMI

## calculate the daily proportion of users who travel outside for cities

```{r}
# exlcude these categories of places
exclude_category <-
  c("", "Residential", "Others", "Education")

# define the time period
period_focus <- c(ymd("2020-01-01"):ymd("2020-05-02"))
period_before_covid <- c(ymd("2020-01-01"):ymd("2020-01-19"))


checkins_nonres <-
  checkins[created_at %in% period_focus] %>%
  .[!(category_google %in% exclude_category)]

# count the users who travelling outside for cities
usercount <-
  checkins_nonres[, .(usercount = uniqueN(userid)), 
                  by = .(created_at, city)] %>%
  .[order(city, created_at)]
```


## calculate Weibo CMI and normalize

```{r}
userprop_nor <-
  usercount[, userprop_nor := 
              (usercount-min(usercount))/(max(usercount)-min(usercount)),
            by = .(city)]

# Note: "Number of users travelling" is directly used here instead of "proportion of users travelling". Considering the need for normalization calculation, the calculation results of the two are consistent.
```


## join population census and administrative data

```{r}
userprop_nor_pop <-
  merge(userprop_nor,
        adm_census,
        all.x = T,
        by.x = "city",
        by.y = "city_join")

# data failed to join
# userprop_nor_pop[city_pinyin == "", unique(city)]
```


## city level: 7MA (7 days moving average) and compute relative value

```{r}
userprop_city_nor <-
  userprop_nor_pop[, .(created_at, 
                       city, 
                       city_pinyin, 
                       userprop_nor_city = userprop_nor)]

userprop_city_nor[order(city, created_at),
                  userprop_nor_city_7MA := 
                    rollmean(userprop_nor_city, k = 7, fill = NA),
                  by = .(city, city_pinyin)]

baseline_raw_city <-
  userprop_city_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_raw = median(userprop_nor_city, na.rm = T)), by = .(city)]

baseline_7MA_city <-
  userprop_city_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(userprop_nor_city_7MA, na.rm = T)), by = .(city)]

userprop_city_relative <-
  merge(userprop_city_nor,
        baseline_raw_city,
        all.x = T,
        by = "city") %>%
  merge(baseline_7MA_city,
        all.x = T,
        by = "city") %>%
  .[, userprop_relative := userprop_nor_city/baseline_raw-1] %>%
  .[, userprop_7MA_relative := userprop_nor_city_7MA/baseline_7MA-1]
```


## select cities

```{r}
# select the abnormal cities
city_abnor <-
  userprop_city_relative[userprop_7MA_relative > 2] %>%
  .[, .(num = .N), by = .(city)]

num_checkins <-
  checkins_nonres[, .(num_checkins = .N), by = .(city)] %>%
  .[order(-num_checkins)]

# select cities with sufficient sample size and exclude abnormal cities
userprop_nor_pop_filter <-
  userprop_nor_pop %>%
  .[city %in% num_checkins[num_checkins > 3000, city]] %>%
  .[!(city %in% city_abnor[, city])]

# the number of selected cities
# userprop_nor_pop_filter$city %>% uniqueN()
```


## weighted aggregate to provincial and national levels

```{r}
# provincial level
userprop_pr_nor <-
  userprop_nor_pop_filter[, .(userprop_nor_pr = 
                         sum(userprop_nor*pop_2020_prop_pr, na.rm = T)),
                   by = .(created_at, pr_join, pr_pinyin)] %>%
  .[order(pr_join, created_at)]

userprop_pr_nor[1:5]


# national level
userprop_na_nor <-
  userprop_nor_pop_filter[, .(userprop_nor_na = 
                         sum(userprop_nor*pop_2020_prop_na, na.rm = T)),
                   by = .(created_at)] %>%
  .[order(created_at)]

userprop_na_nor[1:5]
```


## provincial and national level: 7MA and compute relative value

```{r}
# provincial level
userprop_pr_nor[order(pr_join, created_at),
                userprop_nor_pr_7MA := 
                  rollmean(userprop_nor_pr, k = 7, fill = NA),
                by = .(pr_join, pr_pinyin)]

baseline_raw_pr <-
  userprop_pr_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_raw = median(userprop_nor_pr, na.rm = T)), by = .(pr_join)]

baseline_7MA_pr <-
  userprop_pr_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(userprop_nor_pr_7MA, na.rm = T)), by = .(pr_join)]

userprop_pr_relative <-
  merge(userprop_pr_nor,
        baseline_raw_pr,
        all.x = T,
        by = "pr_join") %>%
  merge(baseline_7MA_pr,
        all.x = T,
        by = "pr_join") %>%
  .[, userprop_relative := userprop_nor_pr/baseline_raw-1] %>%
  .[, userprop_7MA_relative := userprop_nor_pr_7MA/baseline_7MA-1]

# national level
userprop_na_nor[order(created_at),
                userprop_nor_na_7MA := 
                  rollmean(userprop_nor_na, k = 7, fill = NA)]

baseline_raw_na <-
  userprop_na_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_raw = median(userprop_nor_na, na.rm = T))]

baseline_7MA_na <-
  userprop_na_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(userprop_nor_na_7MA, na.rm = T))]

userprop_na_relative <-
  userprop_na_nor[, ':='(baseline_raw = baseline_raw_na$baseline_raw,
                         baseline_7MA = baseline_7MA_na$baseline_7MA)] %>%
  .[, userprop_relative := userprop_nor_na/baseline_raw-1] %>%
  .[, userprop_7MA_relative := userprop_nor_na_7MA/baseline_7MA-1]
```


# calculate Baidu CMI

## normalize the Baidu CMI

```{r}
CMI_nor <-
  CMI[, CMI_nor := (CMI-min(CMI))/(max(CMI)-min(CMI)), by = .(city)]
```


## join population census and administrative data

```{r}
CMI_pop <-
  merge(CMI_nor,
        adm_census,
        all.x = T,
        by.x = "adcode",
        by.y = "adcode_CMI_join")

# cities failed to join population census
# CMI_pop[is.na(pop_2020), unique(ct_name_2)]
```


## weighted aggregate to provincial and national level

```{r}
# provincial level
CMI_pr_nor <-
  CMI_pop[, .(CMI_nor_pr = sum(CMI_nor*pop_2020_prop_pr, na.rm = T)), 
          by = .(date, pr_join, pr_pinyin)]

# national level
CMI_na_nor <-
  CMI_pop[, .(CMI_nor_na = sum(CMI_nor*pop_2020_prop_na, na.rm = T)), 
          by = .(date)]
```


## provincial and national level: 7MA and compute relative value

```{r}
# province level
CMI_pr_nor[order(pr_join, date), 
           CMI_nor_pr_7MA := rollmean(CMI_nor_pr, k = 7, fill = NA), 
           by = .(pr_join)]

baseline_raw_CMI_pr <-
  CMI_pr_nor[date %in% period_before_covid] %>%
  .[, .(baseline_raw = median(CMI_nor_pr, na.rm = T)), by = .(pr_join)]

baseline_7MA_CMI_pr <-
  CMI_pr_nor[date %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(CMI_nor_pr_7MA, na.rm = T)), by = .(pr_join)]

CMI_pr_nor_relative <- 
  merge(CMI_pr_nor,
        baseline_raw_CMI_pr,
        all.x = T,
        by = "pr_join") %>%
  merge(baseline_7MA_CMI_pr,
        all.x = T,
        by = "pr_join") %>%
  .[, CMI_relative := CMI_nor_pr/baseline_raw-1] %>%
  .[, CMI_7MA_relative := CMI_nor_pr_7MA/baseline_7MA-1]

# national level
CMI_na_nor[order(date),
           CMI_nor_na_7MA := rollmean(CMI_nor_na, k = 7, fill = NA)]

baseline_raw_CMI_na <-
  CMI_na_nor[date %in% period_before_covid] %>%
  .[, .(baseline_raw = median(CMI_nor_na, na.rm = T))]

baseline_7MA_CMI_na <-
  CMI_na_nor[date %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(CMI_nor_na_7MA, na.rm = T))]

CMI_na_nor_relative <- 
  CMI_na_nor[, ':='(baseline_raw = baseline_raw_CMI_na$baseline_raw,
                    baseline_7MA = baseline_7MA_CMI_na$baseline_7MA)] %>%
  .[, CMI_relative := CMI_nor_na/baseline_raw-1] %>%
  .[, CMI_7MA_relative := CMI_nor_na_7MA/baseline_7MA-1]
```


# Pearson analysis between Weibo CMI and Baidu CMI

```{r calculate_signifiant_level}
cal_sign <- function(i) {
  if(i < 1e-3){
    return("***")
  } else if(i < 1e-2){
    return("**")
  } else if(i < 5e-2){
    return("*") 
  } else {
    return("")
  }
}
```


```{r}
# provincial level
CMI_weibo_pr <-
  merge(CMI_pr_nor_relative[, .(pr_join,
                                pr_pinyin,
                                date,
                                CMI_relative,
                                CMI_7MA_relative)], 
        userprop_pr_relative[, .(pr_join,
                                 created_at,
                                 userprop_relative,
                                 userprop_7MA_relative)], 
        by.x = c("pr_join", "date"),
        by.y = c("pr_join", "created_at"))

cor_result_pr <-
  CMI_weibo_pr[, .(pr_join, pr_pinyin)] %>%
  unique() %>%
  .[, ':='(cor_value = NA_real_, p_value = NA_real_)]

for(i in 1:nrow(cor_result_pr)){

  pr_analysis <- cor_result_pr[i, pr_join]
  
  pearson_test <-
    cor.test(CMI_weibo_pr[pr_join == pr_analysis, CMI_7MA_relative],
             CMI_weibo_pr[pr_join == pr_analysis, userprop_7MA_relative],
             method = "pearson")
  
  cor_result_pr[i, "cor_value"] <- pearson_test$estimate
  cor_result_pr[i, "p_value"] <- pearson_test$p.value
}

# add label
cor_result_pr %>%
  .[, cor_value_round := round(cor_value, digits = 2)] %>%
  .[, sign_level := NA_character_]

for(i in 1:nrow(cor_result_pr)){
  cor_result_pr[i, sign_level := cal_sign(p_value)]
}

cor_result_pr[, label := paste0("*r*", " = ", 
                                str_pad(cor_value_round,
                                        width = 4,
                                        side = "right",
                                        pad = "0"),
                                "<sup>", sign_level, "</sup>")]


# national level
CMI_weibo_na <-
  merge(CMI_na_nor_relative[, .(date, 
                                CMI_relative,
                                CMI_7MA_relative)], 
        userprop_na_relative[, .(created_at,
                                 userprop_relative,
                                 userprop_7MA_relative)], 
        by.x = c("date"),
        by.y = c("created_at"))

cor_result_na <-
  data.table(cor_value = NA_real_, p_value = NA_real_)
  
cor_result_na[, "cor_value"] <- pearson_test$estimate
cor_result_na[, "p_value"] <- pearson_test$p.value

cor_result_na %>%
  .[, cor_value_round := round(cor_value, digits = 2)] %>%
  .[, sign_level := NA_character_]

for(i in 1:nrow(cor_result_na)){
  cor_result_na[i, sign_level := cal_sign(p_value)]
}

cor_result_na[, label := paste0("*r*", " = ", cor_value_round, "<sup>",
                                sign_level, "</sup>")]
```


# users correction

```{r file_path_users_correction}
ifile_pop_structure_yearbook <-
  "data/raw/figure4_yearbook_2021_city_level_age_gender/population_structure_yearbook2021.csv"

ifile_userinfo <-
  "data/processed/04_userinfo.csv.gz"
```


```{r input_data}
pop_yearbook_structure <-
  fread(ifile_pop_structure_yearbook)

userinfo <-
  fread(ifile_userinfo) %>%
  .[!is.na(gender) & !is.na(age)] %>%
  .[, .(userid, age, gender, location)]
```


```{r data_preprocess}
exclude_location <-
  c("海外", "其他", "香港", "澳门", "台湾", "")

userinfo <-
  userinfo %>%
  .[, age_group := fcase(age >= 0 & age <= 14, "pop_0_14",
                         age >= 15 & age <= 64, "pop_15_64",
                         age >= 65 & age <= 90, "pop_65_above",
                         default = NA)] %>% 
  .[!is.na(age_group)] %>%
  .[str_detect(location, " "), located_pr := str_split_i(location, " ", 1)] %>%
  .[!str_detect(location, " "), located_pr := location] %>%
  .[!(located_pr %in% exclude_location)]
```


## calculate the users correction factor

```{r}
# yearbook
pop_yearbook_prop <-
  pop_yearbook_structure[, pop_nation := sum(pop_region, na.rm = T)] %>%
  .[, ':='(pop_0_14_prop = pop_0_14/pop_nation,
           pop_15_64_prop = pop_15_64/pop_nation,
           pop_65_above_prop = pop_65_above/pop_nation)]

pop_yearbook_prop_melt <-
  melt(pop_yearbook_prop[, .(region_cn, pop_0_14_prop, pop_15_64_prop, pop_65_above_prop)],
       id.vars = "region_cn") %>%
  .[, variable := str_replace(variable, "_prop", "")] %>%
  setnames(old = c("region_cn", "variable", "value"),
           new = c("pr", "age_group", "pop_yearbook_prop"))

# Weibo user
pop_sample_prop <-
  userinfo %>%
  .[, .(pop_sample = .N), by = .(located_pr, age_group)] %>%
  .[, pop_sample_prop := pop_sample/sum(pop_sample, na.rm = T)]

# calculate proportion difference between Weibo users and yearbook statistics
pop_prop_merge <-
  merge(pop_sample_prop[, .(pr = located_pr, age_group, pop_sample_prop)],
        pop_yearbook_prop_melt,
        by = c("pr", "age_group")) %>%
  .[, pop_prop_rec := sqrt(pop_yearbook_prop/pop_sample_prop)]
```


## correct users

```{r}
checkins_nonres_userinfo_adm <-
  merge(checkins_nonres,
        userinfo[, .(userid = as.character(userid), age_group)],
        all.x = T,
        by = "userid") %>%
  .[!is.na(age_group)] %>%
  merge(city_adm[, .(city_join, pr_blog = pr_join, pr_pinyin)],
        all.x = T,
        by.x = "city",
        by.y = "city_join") %>%
  .[!is.na(pr_blog)] %>%
  .[city %in% num_checkins[num_checkins > 3000, city]] %>%
  .[!(city %in% city_abnor[, city])]

usercount_popgroup <-
  checkins_nonres_userinfo_adm[, .(usercount = uniqueN(userid)), 
                              by = .(created_at, age_group, pr_blog, pr_pinyin)]

usercount_popgroup_rec <-
  merge(usercount_popgroup,
        pop_prop_merge[, .(pr, age_group, pop_prop_rec)],
        all.x = T,
        by.x = c("age_group", "pr_blog"),
        by.y = c("age_group", "pr")) %>%
  .[, usercount_rec_pop := usercount*pop_prop_rec] %>%
  .[, .(usercount_rec = sum(usercount_rec_pop, na.rm = T)), 
    by = .(pr_blog, pr_pinyin, created_at)] %>%
  .[order(pr_blog, created_at)]


# province level
usercount_pr_rec <-
  usercount_popgroup_rec

# national level
usercount_na_rec <-
  usercount_popgroup_rec[, .(usercount_rec = sum(usercount_rec)), 
                         by = .(created_at)]
```


## 7MA and compute relative value

```{r}
# provincial level
userprop_pr_rec_nor <-
  usercount_pr_rec[, userprop_rec_nor := 
                           (usercount_rec-min(usercount_rec))/
                           (max(usercount_rec)-min(usercount_rec)),
                         by = .(pr_blog, pr_pinyin)]

userprop_pr_rec_nor[order(pr_blog, created_at),
                    userprop_rec_nor_7MA :=
                      rollmean(userprop_rec_nor, k = 7, fill = NA),
                    by = .(pr_blog, pr_pinyin)]

baseline_raw_rec_pr <-
  userprop_pr_rec_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_raw = median(userprop_rec_nor, na.rm = T)), by = .(pr_blog)]

baseline_7MA_rec_pr <-
  userprop_pr_rec_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(userprop_rec_nor_7MA, na.rm = T)), by = .(pr_blog)]

userprop_rec_pr_relative <-
  merge(userprop_pr_rec_nor,
        baseline_raw_rec_pr,
        all.x = T,
        by = "pr_blog") %>%
  merge(baseline_7MA_rec_pr,
        all.x = T,
        by = "pr_blog") %>%
  .[, userprop_relative := userprop_rec_nor/baseline_raw-1] %>%
  .[, userprop_7MA_relative := userprop_rec_nor_7MA/baseline_7MA-1]

# national level
userprop_na_rec_nor <-
  usercount_na_rec[, userprop_rec_nor := 
                     (usercount_rec-min(usercount_rec))/
                           (max(usercount_rec)-min(usercount_rec))]

userprop_na_rec_nor[order(created_at),
                    userprop_rec_nor_7MA :=
                      rollmean(userprop_rec_nor, k = 7, fill = NA)]

baseline_raw_rec_na <-
  userprop_na_rec_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_raw = median(userprop_rec_nor, na.rm = T))]

baseline_7MA_rec_na <-
  userprop_na_rec_nor %>%
  .[created_at %in% period_before_covid] %>%
  .[, .(baseline_7MA = median(userprop_rec_nor_7MA, na.rm = T))]

userprop_rec_na_relative <-
  userprop_na_rec_nor[, ':='(baseline_raw = baseline_raw_rec_na$baseline_raw,
                             baseline_7MA = baseline_7MA_rec_na$baseline_7MA)] %>%
  .[, userprop_relative := userprop_rec_nor/baseline_raw-1] %>%
  .[, userprop_7MA_relative := userprop_rec_nor_7MA/baseline_7MA-1]
```


# Pearson analysis bwtween corrected Weibo CMI and Baidu CMI

```{r}
# provincial level
CMI_weibo_rec_pr <-
  merge(CMI_pr_nor_relative[, .(pr_join,
                                pr_pinyin,
                                date,
                                CMI_relative,
                                CMI_7MA_relative)], 
        userprop_rec_pr_relative[, .(pr_blog,
                                     created_at,
                                     userprop_relative,
                                     userprop_7MA_relative)], 
        by.x = c("pr_join", "date"),
        by.y = c("pr_blog", "created_at"))

cor_result_rec_pr <-
  CMI_weibo_rec_pr[, .(pr_join, pr_pinyin)] %>%
  unique() %>%
  .[, ':='(cor_value = NA_real_, p_value = NA_real_)]

for(i in 1:nrow(cor_result_rec_pr)){

  pr_analysis <- cor_result_rec_pr[i, pr_join]
  
  pearson_test <-
    cor.test(CMI_weibo_rec_pr[pr_join == pr_analysis, CMI_7MA_relative],
             CMI_weibo_rec_pr[pr_join == pr_analysis, userprop_7MA_relative],
             method = "pearson")
  
  cor_result_rec_pr[i, "cor_value"] <- pearson_test$estimate
  cor_result_rec_pr[i, "p_value"] <- pearson_test$p.value
}

cor_result_rec_pr %>%
  .[, cor_value_round := round(cor_value, digits = 2)] %>%
  .[, sign_level := NA_character_]

for(i in 1:nrow(cor_result_rec_pr)){
  cor_result_rec_pr[i, sign_level := cal_sign(p_value)]
}

cor_result_rec_pr[, label := paste0("*r*",
                                    "<sub>c</sub>", 
                                    " = ", 
                                    str_pad(cor_value_round, 
                                            width = 4, 
                                            side = "right",
                                            pad = "0"), 
                                    "<sup>", sign_level, "</sup>")]

# national level
CMI_weibo_rec_na <-
  merge(CMI_na_nor_relative[, .(date, 
                                CMI_relative,
                                CMI_7MA_relative)], 
        userprop_rec_na_relative[, .(created_at,
                                     userprop_relative,
                                     userprop_7MA_relative)], 
        by.x = c("date"),
        by.y = c("created_at"))

cor_result_rec_na <-
  data.table(cor_value = NA_real_, p_value = NA_real_)
  
cor_result_rec_na[, "cor_value"] <- pearson_test$estimate
cor_result_rec_na[, "p_value"] <- pearson_test$p.value

cor_result_rec_na %>%
  .[, cor_value_round := round(cor_value, digits = 2)] %>%
  .[, sign_level := NA_character_]

for(i in 1:nrow(cor_result_rec_na)){
  cor_result_rec_na[i, sign_level := cal_sign(p_value)]
}

cor_result_rec_na[, label := paste0("*r*", "<sub>c</sub>", 
                              " = ", cor_value_round, "<sup>",
                              sign_level, "</sup>")]
```


# plot the Pearson analysis result

## prepare plotdata

```{r}
# provincial level
CMI_baidu_nonrec_rec_pr <-
  merge(CMI_weibo_rec_pr %>%
          setnames(old = c("userprop_relative",
                           "userprop_7MA_relative"),
                   new = c("userprop_rec_relative",
                           "userprop_rec_7MA_relative"),
                   skip_absent = T),
        CMI_weibo_pr[, !c("CMI_relative", "CMI_7MA_relative")],
        all.x = T,
        by = c("pr_join", "date", "pr_pinyin")) %>%
  .[!is.na(CMI_relative) & 
      !is.na(CMI_7MA_relative) &
      !is.na(userprop_relative) &
      !is.na(userprop_7MA_relative) &
      !is.na(userprop_rec_relative) &
      !is.na(userprop_rec_7MA_relative)] %>%
  .[pr_join %in% cor_result_rec_pr[, pr_join]] %>%
  melt(id.vars = c("pr_join", "pr_pinyin", "date")) %>%
  .[, variable := factor(variable,
                         levels = c("CMI_relative",
                                    "CMI_7MA_relative",
                                    "userprop_relative",
                                    "userprop_7MA_relative",
                                    "userprop_rec_relative",
                                    "userprop_rec_7MA_relative"))]

cor_result_nonrec_rec_pr <-
  merge(cor_result_rec_pr[, .(pr_pinyin, label_rec = label)],
        cor_result_pr[, .(pr_pinyin, label_raw = label)],
        all.x = T, 
        by = "pr_pinyin")

# national level
CMI_baidu_nonrec_rec_na <-
  merge(CMI_weibo_rec_na %>%
          setnames(old = c("userprop_relative",
                           "userprop_7MA_relative"),
                   new = c("userprop_rec_relative",
                           "userprop_rec_7MA_relative"),
                   skip_absent = T),
        CMI_weibo_na[, !c("CMI_relative", "CMI_7MA_relative")],
        all.x = T,
        by = c("date")) %>%
  .[!is.na(CMI_relative) & 
      !is.na(CMI_7MA_relative) &
      !is.na(userprop_relative) &
      !is.na(userprop_7MA_relative) &
      !is.na(userprop_rec_relative) &
      !is.na(userprop_rec_7MA_relative)] %>%
  melt(id.vars = c("date")) %>%
  .[, variable := factor(variable,
                         levels = c("CMI_relative",
                                    "CMI_7MA_relative",
                                    "userprop_relative",
                                    "userprop_7MA_relative",
                                    "userprop_rec_relative",
                                    "userprop_rec_7MA_relative"))]

cor_result_nonrec_rec_na <-
  cbind(cor_result_rec_na[, .(label_rec = label)],
        cor_result_na[, .(label_raw = label)])

# plotdata
CMI_baidu_nonrec_rec <-
  rbind(CMI_baidu_nonrec_rec_pr,
        CMI_baidu_nonrec_rec_na[, ':='(pr_join = "全国", pr_pinyin = "Nation")])

pr_pinyin_order <-
  CMI_baidu_nonrec_rec$pr_pinyin[CMI_baidu_nonrec_rec$pr_pinyin != "Nation"] %>%
  unique() %>%
  sort()

CMI_baidu_nonrec_rec$pr_pinyin <-
  factor(CMI_baidu_nonrec_rec$pr_pinyin, levels = c("Nation", pr_pinyin_order))


cor_result_nonrec_rec <-
  rbind(cor_result_nonrec_rec_pr,
        cor_result_nonrec_rec_na[, ':='(pr_pinyin = "Nation")])

cor_result_nonrec_rec$pr_pinyin <-
  factor(cor_result_nonrec_rec$pr_pinyin, levels = c("Nation", pr_pinyin_order))
```


## plot the esult

```{r}
plot <-
  ggplot(CMI_baidu_nonrec_rec) +
  geom_line(mapping = aes(x = date, 
                          y = value, 
                          color = variable,
                          linewidth = variable)) +
  geom_richtext(data = cor_result_nonrec_rec,
                mapping = aes(x = ymd("2020-05-10"),
                              y = 0.8,
                              label = label_raw),
                size = 2.5,
                lineheight = 1,
                hjust = "inward",
                fill = NA,
                label.color = NA) +
  geom_richtext(data = cor_result_nonrec_rec,
                mapping = aes(x = ymd("2020-05-10"),
                              y = 0.4,
                              label = label_rec),
                size = 2.5,
                lineheight = 1,
                hjust = "inward",
                fill = NA,
                label.color = NA) +
  geom_hline(yintercept = 0,
             color = "black",
             linetype = "solid",
             # size = 0.5,
             alpha = 0.5) +
  geom_vline(xintercept = ymd("2020-01-20"),
             color = "red",
             linetype = "dashed",
             linewidth = 0.3) +
  scale_color_manual(
    values = c("CMI_relative" = color_secondary[6],
               "CMI_7MA_relative" = color_primary[6],
               "userprop_relative" = color_secondary[4],
               "userprop_7MA_relative" = color_primary[4],
               "userprop_rec_relative" = color_secondary[2],
               "userprop_rec_7MA_relative" = color_primary[2]), 
    labels = c(
      "CMI_relative" = "Baidu indice",
      "CMI_7MA_relative" = "Baidu indice (7MA)",
      "userprop_relative" = "Weibo indice",
      "userprop_7MA_relative" = "Weibo indice (7MA)",
      "userprop_rec_relative" = "Weibo indice (corrected)",
      "userprop_rec_7MA_relative" = "Weibo indice (corrected, 7MA)")
    ) +
  scale_linewidth_manual(
    values = c("CMI_relative" = 0.1,
               "CMI_7MA_relative" = 0.35,
               "userprop_relative" = 0.1,
               "userprop_7MA_relative" = 0.35,
               "userprop_rec_relative" = 0.1,
               "userprop_rec_7MA_relative" = 0.35)
  ) +
  scale_x_date(breaks = ymd(c("2020-01-01",
                              "2020-02-01",
                              "2020-03-03",
                              "2020-04-01",
                              "2020-05-01")),
               date_labels = "%b") +
  scale_y_continuous(breaks = seq(-1, 1, 0.5),
                     limits = c(-1, 1),
                     labels = c("-100%", "-50%", "0", "+50%", "+100%")) +
  facet_wrap(~ pr_pinyin, ncol = 6) +
  labs(y = "Percentage change of City Movement Intensity index") +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text = element_text(size = 7),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(t = -70, r = -140, b = 10),
    legend.text = element_text(size = 9),
    legend.spacing.x = unit(0.3, 'cm'),
    legend.key.width = unit(1.0, "cm"),
    strip.background = element_rect(fill = NA, color = NA),
    strip.text = element_text(margin = margin(t = 0, b = 3), size = 8),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.spacing.x = unit(12, "pt")
    ) +
  guides(colour = guide_legend(nrow = 3, override.aes = list(linewidth = 1)),
         linewidth = guide_none())
```


```{r save_plot, eval=FALSE}
figure_name <- "figure4.pdf"

ggsave(filename = figure_name,
       plot = plot,
       path = odir_plot,
       width = 180,
       height = 150,
       units = "mm",
       dpi = 300)
```






